The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

###Neccesary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

@@

3. Positive reinforcement: This is easier to define than self-confience, but it is also culture-dependent (individual-focused systems vs group-oriented ones). This will also need to be quantified for the qualitative portion of this project.

>>>>

###Necessary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

@@

3. Positive reinforcement: This can possibly be computed as an index and characterized on a scale even if this is not easy to quantify.
